An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-07-08 jmiv.tex
fatigue

\subsection{Outline}
Section~2 reviews the concept of multigrid convergence and highlights
its importance for the definition of digital estimators. We describe
two convergent estimators used in this paper, one that approaches the
length of elementary discrete contour elements, and the other that
approaches the curvature of a discrete contour. They are used in the
optimization model and in the definition of the digital
elastica. Section~3 describes a local combinatorial optimization model
suitable for different curvature estimators, that presents interesting
results but is too costly in practice. Section~4 describes the
proposed Elastica-driven curvature evolution model along with several
illustrations of digital flows. Section~5 explains how to use this
evolution model as a post-processing step in an image segmentation
framework and compares it to two related approaches. We conclude and
draw some perspectives to this work in Section~6.

@@

\begin{figure}[hp!]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-square-concavities-probe.eps}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-flower-concavities-probe.eps}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for different radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}

@@

We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE acts as a
contour correction method. Here we are going to use a data fidelity term in order to characterize the object of
interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color
intensities $G_f$ and $G_b$, and we define the data fidelity term as the cross-entropy, i.e.

@@

\daniel{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization. The curvature can fill gaps and is smoother than the one produced by length only, resulting in more pleasant segmentations. In figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation produced by GrabCut and Schoenemann's method. Our method is successful in producing curvature regularized segmentations and demonstrates the completion property of curvature. Moreover, it does not suffer from over segmentation, it is faster than Schoenemann's, and in several opportunities produces better segmentations than GrabCut.}

@@

We have studied in depth several digital curve evolution models based
on the Elastica energy and we have presented an application of one of
them to image segmentation. The processes we have described are
completely digital, and do not suffer from issues that typically
arises in models that passes through a discretization stage, as
rounding. Moreover, the model can handle changes in topology and its
results are competitive with similar approaches while achieving
reasonable running times.

Future developments of this work may include automatization, no more
dependence on seeds selected by the user and automatic choice of ball
estimation radius based on the reach of the shape. One can also think
to extend the DCE algorithm to $3$d, as the integral invariant
estimator preserves its properties in that space. In future works, a
denoising application may be derived by running the flow on the $3$d
shape with data fidelity defined by image intensities or by distance
to initial position.

>>>>

\subsection{Outline}
Section~2 reviews the concept of multigrid convergence and highlights
its importance for the definition of digital estimators. We describe
two convergent estimators used in this paper, one that approaches the
length of elementary discrete contour elements, and the other that
approaches the curvature of a discrete contour. They are used in the
optimization model and in the definition of the digital
elastica. Section~3 describes a local combinatorial optimization model
suitable for several curvature estimators, that presents interesting
results but is too costly in practice. Section~4 describes the
proposed Elastica-driven curvature evolution model along with several
illustrations of digital flows. Section~5 explains how to use this
evolution model as a post-processing step in an image segmentation
framework and compares it to two related approaches. We conclude and
draw some perspectives to this work in Section~6.

@@

\begin{figure}[hp!]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-square-concavities-probe.eps}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-flower-concavities-probe.eps}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for varying radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}

@@

We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE acts as a
contour correction method. Here we use a data fidelity term in order to characterize the object of
interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color
intensities $G_f$ and $G_b$, and we define the data fidelity term as the cross-entropy, i.e.

@@

{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a
  pure length regularization. The curvature can fill gaps and is smoother than the one produced by length only,
  resulting in more pleasant segmentations. In figures \ref{fig:segmentation-results} and
  \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation
  produced by GrabCut and Schoenemann's method. Our method is successful in producing curvature regularized
  segmentations and demonstrates the completion property of curvature. Moreover, it does not suffer from over
  segmentation, it is much faster than Schoenemann's, and in several opportunities produces better segmentations than
  GrabCut.

@@

We have studied in depth several digital curve evolution models based on a digital version of the Elastica energy and we
have presented an application to image segmentation. The processes we have described are completely digital, and do not
suffer from issues that typically arise in models that passes through a discretization stage, such as
rounding. Moreover, the model can handle changes in topology and its results are competitive with similar approaches
while achieving reasonable running times.

Future developments of this work will include extending the DCE algorithm to $3$d, as the integral invariant estimator
is available in higher dimensions. As a result, a denoising application may be derived by lifting the flow to $3$d
with a data fidelity defined by image intensities or by distance to initial position.
